---
title: "Notes on Project"
author: "Joël Meili"
date: "27 September 2018"
output:
  md_document:
    variant: markdown_github
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(gridExtra)
source('read_data.R')
```

# First Step - Value-at-Risk
- We first calculated the Value-at-Risk for all asset classes at confidence intervals of 84%, 97.5% and 99.9%. The result is shown in the following table:

```{r echo=F}
data.var <- data.var %>% spread(VaR, Value)
data.var$Horizon <- factor(data.var$Horizon, c("Daily", "Weekly", "Monthly", "Yearly"))
data.var %>% arrange(Asset, Horizon) %>% kable() %>% kable_styling()
```

- Then we calculated the distribution of e.g. daily returns on all asset classes and then compared it with a normal distribution

```{r echo=F}
grid.arrange(h.daily, h.weekly, h.monthly, h.yearly, nrow=2)
grid.arrange(qq.daily, qq.weekly, qq.monthly, qq.yearly, nrow=2)

```

- Then we used the Anderson-Darling test to measure normality of the return data on the different time horizons

```{r echo=F}
p.values %>% kable() %>% kable_styling()
```




