---
title: "Notes on Project"
author: "Joël Meili"
date: "27 September 2018"
output:
  md_document:
    variant: markdown_github
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(gridExtra)
source('read_data.R')
```

# 1. Step - Value-at-Risk
- We first calculated the Value-at-Risk for all asset classes at confidence intervals of 84%, 97.5% and 99.9%. The result is shown in the following table:

```{r echo=F}
data.var %>% group_by(Asset) %>% kable() %>% kable_styling()
```
- Then we calculated the distribution of e.g. daily returns on all asset classes and then compared it with a normal distribution
- We observed that the distributions follow the assumptions of normal distributed returns almost perfectly
- Although we can observe a fat tailed distribution on S&P 500 on yearly returns and also a bimodal distribution on JPY on yearly returns

```{r echo=F}
grid.arrange(g.daily, g.weekly, g.monthly, g.yearly, nrow=2)
```





